---
title: "XGBoost wrapper"
output: html_notebook
---

# XGBoost wrapper for seurat project in R

```{r}
source("tianfengRwrappers.R")
library(xgboost)
library(Matrix)
library(mclust)
library(tidyverse)
library(SHAPforxgboost)
library(lambda.r)

ds0 <- readRDS("ds0.rds")
ds1 <- readRDS("ds1.rds")
ds2 <- readRDS("ds2.rds")
```


```{r}
XGBoost_train_from_seuobj <- function(seuobj, is_highvar = T, test_ratio = 0.3, seed = 7)
{ 
  ## set test_ratio to 0 to avoid extracting test from dataset
  set.seed(seed)
  seuobj_label <- as.numeric(as.character(Idents(seuobj)))
  if(is.na(seuobj_label[1])) # check vaild Idents
  {
    stop("Please ensure that seurat idents are in numeric forms")
  }
  # colnames(seuobj_data) <- NULL
  seuobj_data <- get_data_table(seuobj, highvar = T, type = "data")
  xgb_param <- list(eta = 0.2, max_depth = 6, 
                    subsample = 0.6,  num_class = length(table(Idents(seuobj))),
                    objective = "multi:softprob", eval_metric = 'mlogloss')
  
  if(test_ratio == 0) {
    seuobj_train_data <- list(data = t(as(seuobj_data,"dgCMatrix")), label = seuobj_label) 
    # use whole dataset as train data
    seuobj_train <- xgb.DMatrix(data = seuobj_train_data$data,label = seuobj_train_data$label)
    bst_model <- xgb.train(xgb_param, seuobj_train, nrounds = 100, verbose = 0)
  } else {
    index <- c(1:dim(seuobj_data)[2]) %>% sample(ceiling(test_ratio*dim(seuobj_data)[2]), replace = F, prob = NULL)
    seuobj_train_data <- list(data = t(as(seuobj_data[,-index],"dgCMatrix")), label = seuobj_label[-index])
    seuobj_test_data <- list(data = t(as(seuobj_data[,index],"dgCMatrix")), label = seuobj_label[index])
    seuobj_test <- xgb.DMatrix(data = seuobj_test_data$data,label = seuobj_test_data$label)
    seuobj_train <- xgb.DMatrix(data = seuobj_train_data$data,label = seuobj_train_data$label)
    watchlist <- list(train = seuobj_train, eval = seuobj_test)
    bst_model <- xgb.train(xgb_param, seuobj_train, nrounds = 100, watchlist, verbose = 0)
  }
  return(bst_model)
}
# saveRDS(bst_model, "ds2_model.rds")

show_train_loss <- function(bst_model, nrounds = 100) #when $ test_ratio \neq 0 $ show loss in watchlist
{
  eval_loss <- bst_model[["evaluation_log"]][["eval_mlogloss"]]
  plot_ly(data.frame(eval_loss), x = c(1:nrounds), y = eval_loss) %>% 
    add_trace(type = "scatter", mode = "markers+lines", 
              marker = list(color = "black", line = list(color = "#1E90FFC7", width = 1)),
              line = list(color = "#1E90FF80", width = 2)) %>% 
    layout(xaxis = list(title = "epoch"),yaxis = list(title = "eval_mlogloss"), 
           title = "train_loss", font = list(family = "Arial", size = 25, color = "black"))
}

XGBoost_predict_from_seuobj <- function(seuobj, bst_model, is_highvar = T, seed = 7, celltype_assign = 2)
{
  #return a updated seurat object with new metadata named confidence and projected_idents
  seuobj_label <- as.numeric(as.character(Idents(seuobj)))
  if(!is.null(which(is.na(seuobj_label)))) # check vaild Idents
  {
    warning("Please ensure that seurat idents are in numeric forms") #这里似乎不跳出也可以
    seuobj_label <- as.numeric(as.character(seuobj$seurat_clusters))
  }
  temp <- get_data_table(seuobj, highvar = T, type = "data")
  seuobj_data <- matrix(data = 0, nrow = bst_model$nfeatures, ncol = length(colnames(temp)), 
                     byrow = FALSE, dimnames = list(bst_model[["feature_names"]],colnames(temp)))
  intersect_features <- intersect(bst_model[["feature_names"]], rownames(temp))
  seuobj_data[intersect_features,] <- temp[intersect_features,]
  rm(temp)
  

  # colnames(seuobj_data) <- NULL
  seuobj_test_data <- list(data = t(as(seuobj_data,"dgCMatrix")), label = seuobj_label)
  seuobj_test <- xgb.DMatrix(data = seuobj_test_data$data,label = seuobj_test_data$label)
  
  #预测结果
  predict_seuobj_test <- predict(bst_model, newdata = seuobj_test)
  
  predict_prop_seuobj <<- matrix(data=predict_seuobj_test, nrow = bst_model[["params"]][["num_class"]], 
                             ncol = ncol(seuobj), byrow = FALSE, 
                             dimnames = list(as.character(0:(bst_model[["params"]][["num_class"]]-1)),
                                             colnames(seuobj)))

  # predict cell types
  if(celltype_assign == 1){
    seuobj_res <- apply(predict_prop_seuobj,2,ident_assignfunc,rownames(predict_prop_seuobj))
  }else if(celltype_assign == 2){
    seuobj_res <- apply(predict_prop_seuobj,2,ident_assignfunc2,rownames(predict_prop_seuobj))
  }
  
  print(paste('ARI =',adjustedRandIndex(seuobj_res, seuobj_test_data$label)))
  
  seuobj <- AddMetaData(seuobj, data.frame(t(predict_prop_seuobj), stringsAsFactors=F))
  print("return a seurat object with meta.data'X1'~'Xn'")
  
  #save and update seurat object
  seuobj$projected_idents <- factor(seuobj_res, levels =
                                      c(as.character(0:(bst_model[["params"]][["num_class"]]-1)),"unassigned"))
  print("return a seurat object with meta.data'projected_idents'")
  return(seuobj)
}

## assign cell type predicted via tree models, consider confidence
ident_assignfunc <- function(s, ident) {
    if (max(s) > 1.5 / length(ident)) {
          return(ident[which(s == max(s))])
      } else {
          return("unassigned")
      }
}

ident_assignfunc2 <- function(s, ident)
# confidence : max - 2th_max > 0.4
{
    if (max(s) - max(s[s!=max(s)]) > 0.4) {
          return(ident[which(s == max(s))])
      } else {
          return("unassigned")
      }
}

project2ref_celltype <- function(query_seuobj, ref_seuobj, 
                                 query_labels = "projected_idents",
                                 ref_labels = c("seurat_clusters","Classification1")) 
  # transfer lables: add ref_celltype to meta.data in query seurat object
{
  identmap <- levels(ref_seuobj@meta.data[[ref_labels[1]]]) 
  ## build mapping between numeric labels and ref labels
  names(identmap) <- levels(ref_seuobj@meta.data[[ref_labels[2]]]) 
  
  df <- query_seuobj@meta.data[[query_labels]]
  lambda(x,identmap) %:=% ifelse(x=="unassigned",x,names(identmap[identmap == x]))
  levels(df) <- lapply(levels(df), lambda, identmap) %>% as.character() # permute cell labels via `identmap`
  query_seuobj$ref_celltype <- df
  return(query_seuobj)
}

```

---
## function instance
### train
```{r}
umapplot(ds2, group.by = "seurat_clusters")
Idents(ds2) <- ds2$seurat_clusters
bst_model <- XGBoost_train_from_seuobj(ds2)
show_train_loss(bst_model)
```

## function instance
### predict
```{r}
Idents(ds0) <- ds0$seurat_clusters
ds0 <- XGBoost_predict_from_seuobj(ds0, bst_model = bst_model) %>% 
  project2ref_celltype(ref_seuobj = ds2, ref_labels = c("seurat_clusters","Classification1"))

ds1 <- XGBoost_predict_from_seuobj(ds1, bst_model = bst_model) %>% 
  project2ref_celltype(ref_seuobj = ds2, ref_labels = c("seurat_clusters","Classification1"))
umapplot(ds0, group.by = "ref_celltype")

```
## scmap wrapper
```{r}
library(SingleCellExperiment)
library(scmap)

mkref_scmap_from_seuobj <- function(ref_seuobj){
  # return a ref sce object
  ref_sce <- as.SingleCellExperiment(ref_seuobj)
  logcounts(ref_sce) <- log2(counts(ref_sce) + 1)
  
  counts(ref_sce) <- as.matrix(counts(ref_sce))
  logcounts(ref_sce) <- as.matrix(logcounts(ref_sce))
  
  rowData(ref_sce)$feature_symbol <- rownames(ref_sce)
  ref_sce <- ref_sce[!duplicated(rownames(ref_sce)), ]
  ref_sce <- selectFeatures(ref_sce, suppress_plot = T) %>% indexCell()

  return(ref_sce)
}

query_scmap_from_refsce <- function(query_seuobj, ref_sce, ref_labels = 'Classification1'){
  #return a updated seurat object with new metadata named scmap_idents
  
  query_sce <- as.SingleCellExperiment(query_seuobj)
  logcounts(query_sce) <- log2(counts(query_sce) + 1)
  
  counts(query_sce) <- as.matrix(counts(query_sce))
  logcounts(query_sce) <- as.matrix(logcounts(query_sce))
  
  rowData(query_sce)$feature_symbol <- rownames(query_sce)
  query_sce <- query_sce[!duplicated(rownames(query_sce)), ]
  query_sce <- selectFeatures(query_sce, suppress_plot = T) %>% indexCell()
  
  scmapCell_results <- scmapCell(query_sce, list(ref = metadata(ref_sce)$scmap_cell_index))
  scmapCell_clusters <- scmapCell2Cluster(scmapCell_results,
                                          list(as.character(colData(ref_sce)[[ref_labels]])))
  
  query_seuobj$scmap_idents <- data.frame(scmapCell_clusters$scmap_cluster_labs[,"ref"],
                                        row.names = colnames(query_seuobj))
  return(query_seuobj)
}
```

```{r}
ref_sce <- mkref_scmap_from_seuobj(ds2)
ds0 <- query_scmap_from_refsce(ds0, ref_sce)
ds1 <- query_scmap_from_refsce(ds1, ref_sce)
umapplot(ds0, group.by = "scmap_idents")
umapplot(ds0, group.by = "ref_celltype")
table(ds0$ref_celltype)
table(ds0$scmap_idents)
adjustedRandIndex(ds0$ref_celltype, ds0$seurat_clusters)
adjustedRandIndex(ds0$scmap_idents, ds0$seurat_clusters)

```



## supervised vs unsupervised clustering
### upset plot
#### SMC2
```{r}
# library(UpSetR)

df <- cbind(ds1[["Classification1"]],ds1[["ref_celltype"]],ds1[["scmap_idents"]])
df <- df[df$Classification1 == "SMC2" | df$ref_celltype == "SMC2" | df$scmap_idents == "SMC2" ,]
li <- table(df) %>% as.data.frame() #获得含有SMC2的frequency
li <- li[!(li$Freq < 5),] #删除frequency<5的行
li <- li[order(li$Freq,decreasing = T),]
dd <- data.frame(li,index = as.character(1:nrow(li)))

dd$index <- factor(dd$index,levels = 1:length(levels(dd$index)))
dd$Freq <- NULL
dd <- reshape2::melt(dd,id.var = "index")
colnames(dd) <- c("index","type","name")

dt <- data.frame(Freq = li$Freq,index = as.character(1:nrow(li)))
dt$index <- factor(dt$index,levels = 1:length(levels(dt$index)))
dt$col <- dt$Freq>(sum(dt$Freq)/10) #set the color to red for those frequency > 0.1

p1 <- ggplot(dd)+geom_point(mapping = aes(x = index, y = type, color = name), size = 6) + mytheme2 + scale_color_manual(values = colors_list) + theme(axis.ticks.x = element_blank(),axis.title.x = element_blank())
p2 <- ggplot(dt,aes(x = index, y = Freq, fill = col))+geom_bar(stat = "identity") + mytheme2 + theme(axis.ticks.x = element_blank(),axis.title.x = element_blank(), legend.position = 'none') + scale_fill_manual(values = c("black","red"))
 
plot <- cowplot::plot_grid(p2,p1,ncol = 1,align = 'v',rel_heights = c(2,1))
plot
# ggsave("SMC2cells.svg",plot=plot,device = svg,height = 8,width = 8)
```

#### SMC1
```{r}
df <- cbind(ds1[["Classification1"]],ds1[["ref_celltype"]],ds1[["scmap_idents"]])
df <- df[df$Classification1 == "SMC1" | df$ref_celltype == "SMC1" | df$scmap_idents == "SMC1" ,]
li <- table(df) %>% as.data.frame() #获得含有SMC1的frequency
li <- li[!(li$Freq < 5),] #删除frequency<5的行
li <- li[order(li$Freq,decreasing = T),]
dd <- data.frame(li,index = as.character(1:nrow(li)))

dd$index <- factor(dd$index,levels = 1:length(levels(dd$index)))
dd$Freq <- NULL
dd <- reshape2::melt(dd,id.var = "index")
colnames(dd) <- c("index","type","name")

dt <- data.frame(Freq = li$Freq,index = as.character(1:nrow(li)))
dt$index <- factor(dt$index,levels = 1:length(levels(dt$index)))
dt$col <- dt$Freq>(sum(dt$Freq)/10) #set the color to red for those frequency > 0.1

p1 <- ggplot(dd)+geom_point(mapping = aes(x = index, y = type, color = name), size = 6) + mytheme2 + scale_color_manual(values = colors_list) + theme(axis.ticks.x = element_blank(),axis.title.x = element_blank())
p2 <- ggplot(dt,aes(x = index, y = Freq, fill = col))+geom_bar(stat = "identity") + mytheme2 + theme(axis.ticks.x = element_blank(),axis.title.x = element_blank(), legend.position = 'none') + scale_fill_manual(values = c("black","red"))
 
plot <- cowplot::plot_grid(p2,p1,ncol = 1,align = 'v',rel_heights = c(2,1))
plot
ggsave("SMC1cells.svg",plot=plot,device = svg,height = 8,width = 8)
```

#### FBM
```{r}
df <- cbind(ds1[["Classification1"]],ds1[["ref_celltype"]],ds1[["scmap_idents"]])
df <- df[df$Classification1 == "Fibromyocyte" | df$ref_celltype == "Fibromyocyte" | df$scmap_idents == "Fibromyocyte" ,]
li <- table(df) %>% as.data.frame() #获得含有Fibromyocyte的frequency
li <- li[!(li$Freq < 5),] #删除frequency<5的行
li <- li[order(li$Freq,decreasing = T),]
dd <- data.frame(li,index = as.character(1:nrow(li)))

dd$index <- factor(dd$index,levels = 1:length(levels(dd$index)))
dd$Freq <- NULL
dd <- reshape2::melt(dd,id.var = "index")
colnames(dd) <- c("index","type","name")

dt <- data.frame(Freq = li$Freq,index = as.character(1:nrow(li)))
dt$index <- factor(dt$index,levels = 1:length(levels(dt$index)))
dt$col <- dt$Freq>(sum(dt$Freq)/10) #set the color to red for those frequency > 0.1

p1 <- ggplot(dd)+geom_point(mapping = aes(x = index, y = type, color = name), size = 6) + mytheme2 + scale_color_manual(values = colors_list) + theme(axis.ticks.x = element_blank(),axis.title.x = element_blank())
p2 <- ggplot(dt,aes(x = index, y = Freq, fill = col))+geom_bar(stat = "identity") + mytheme2 + theme(axis.ticks.x = element_blank(),axis.title.x = element_blank(), legend.position = 'none') + scale_fill_manual(values = c("black","red"))
 
plot <- cowplot::plot_grid(p2,p1,ncol = 1,align = 'v',rel_heights = c(2,1))
plot
ggsave("Fibromyocytecells.svg",plot=plot,device = svg,height = 8,width = 8)
```

## correlation plot
```{r}
scmap <- ds1$scmap_idents
xgb <- ds1$ref_celltype
ref <- ds2$Classification1

geneset1 <- read.table("SMC")
ds1 <- AddModuleScore(ds1,features = geneset1, name = 'SMC_score')
ds2 <- AddModuleScore(ds2,features = geneset1, name = 'SMC_score')
geneset2 <- read.table("FB")
ds1 <- AddModuleScore(ds1,features = geneset2, name = 'FB_score')
ds2 <- AddModuleScore(ds2,features = geneset2, name = 'FB_score')
# f("SMC_score1",label = F, ds1) + scale_colour_gradient(low="#1E90FF", high="#ff2121")
# f("SMC_score1",label = F, ds2) + scale_colour_gradient(low="#1E90FF", high="#ff2121")

df1 <- data.frame(FetchData(ds1, c("SMC_score1","FB_score1"), cells = names(scmap[scmap == "Fibromyocyte"])),type = "scmap") 
df2 <- data.frame(FetchData(ds1,c("SMC_score1","FB_score1"), cells = names(xgb[xgb == "Fibromyocyte"])),type = "xgbtree") 
df3 <- data.frame(FetchData(ds2,c("SMC_score1","FB_score1"), cells = names(ref[ref == "Fibromyocyte"])),type = "reference") 

df <- rbind(df1,df2,df3)

ggboxplot(df, x = "type", y = "SMC_score1", color = "type", add = "jitter") +
  stat_compare_means(comparisons =
                       list(c("scmap","reference"),c("xgbtree","reference")), 
                     method = "wilcox.test") 

ggboxplot(df, x = "type", y = "FB_score1", color = "type", add = "jitter") +
  stat_compare_means(comparisons =
                       list(c("scmap","reference"),c("xgbtree","reference")), 
                     method = "wilcox.test") 

df <- data.frame(row.names = selected_features)
for(cell_type in c("SMC1","Fibromyocyte","SMC2")){
  df1 <- data.frame(FetchData(ds1, selected_features, cells = names(scmap[scmap == cell_type]))) %>% colMeans() 
  df2 <- data.frame(FetchData(ds1, selected_features, cells = names(xgb[xgb == cell_type]))) %>% colMeans()
  df3 <- data.frame(FetchData(ds2, selected_features, cells = names(ref[ref == cell_type]))) %>% colMeans()
  df[paste0("ref_",cell_type)] <- df3
  df[paste0("xgb_",cell_type)] <- df2
  df[paste0("scmap_",cell_type)] <- df1
}

corr <- cor(df)
pheatmap::pheatmap(corr,breaks = unique(c(seq(0.6, 1, length = 100))),
        color = colorRampPalette(c("#1E90FF", "white", "#ff2121"))(100),
        border_color = NA, cluster_rows = T, cluster_cols = T,
        main = "corr", angle_col = 45, show_rownames = T)

library(ggcor)
quickcor(df, type = "upper") + geom_circle2()
```
### PCA
```{r}
selected_features <-intersect(FindVariableFeatures(ds1, nfeatures = 200)@assays[["SCT"]]@var.features,
                              FindVariableFeatures(ds2, nfeatures = 200)@assays[["SCT"]]@var.features)

selected_features <- read.csv("./datatable/ds2_features.csv")
selected_features <- as.character(selected_features$Feature[1:50])
selected_features <- intersect(selected_features, VariableFeatures(ds1))
res <- data.frame(row.names = c("A","B","C"))

for(cell_type in c("SMC1","Fibromyocyte","SMC2")){
  df1 <- data.frame(FetchData(ds1, selected_features, cells = names(scmap[scmap == cell_type])),type = "scmap") 
  df2 <- data.frame(FetchData(ds1,selected_features, cells = names(xgb[xgb == cell_type])),type = "xgbtree") 
  df3 <- data.frame(FetchData(ds2,selected_features, cells = names(ref[ref == cell_type])),type = "reference") 
  
  df <- rbind(df1,df2,df3)
  
  PCAres <- FactoMineR::PCA(df[,c(-ncol(df))],ncp = 5, graph = F)
  
  dd <- cbind(PCAres[["ind"]][["coord"]],data.frame(type = df[,c(ncol(df))]))
  
  # ggplot(dd)+geom_point(aes(x = Dim.1, y = Dim.2, color = type))
  v_scmap <- dd[dd$type == "scmap",c(1:5)] %>% colMeans() %>% as.matrix()
  v_xgb <- dd[dd$type == "xgbtree",c(1:5)] %>% colMeans() %>% as.matrix()
  v_ref <- dd[dd$type == "reference",c(1:5)] %>% colMeans() %>% as.matrix()
  v <- c(norm(v_scmap-v_ref),norm(v_xgb-v_ref),norm(v_xgb-v_scmap))
  res[cell_type] <- v
}
res
```


## unsupervised version
```{r}
umapplot(ds1)
umapplot(ds2)
umapplot(ds0)

bst_model <- XGBoost_train_from_seuobj(ds0)
ds2 <- XGBoost_predict_from_seuobj(ds2,bst_model,celltype_assign = 1)
# Idents(ds2) <- ds2$seurat_clusters
bst_model <- XGBoost_train_from_seuobj(ds2)
ds0 <- XGBoost_predict_from_seuobj(ds0,bst_model,celltype_assign = 1)

umapplot(ds2,group.by = "projected_idents")
confuse_matrix <- table(ds2$seurat_clusters, ds2$projected_idents, dnn=c("true","pre"))

sankey_plot(confuse_matrix = confuse_matrix,
            dimnames(confuse_matrix)$pre,dimnames(confuse_matrix)$true,
            session = "ds2 is projected to ds1")

# choose train dataset (merged)

df <- cbind(ds2[["seurat_clusters"]],ds2[["projected_idents"]])
li <- table(df) %>% as.data.frame() 
li <- li[!(li$Freq < 50),] #删除frequency<50的细胞类型组合
li <- li[order(li$Freq,decreasing = T),]
dd <- data.frame(li,index = as.character(1:nrow(li)))


confuse_matrix[confuse_matrix<50] <- 0 #删除frequency<50的细胞类型
confuse_matrix


# find embedding pattern
temp <- prop.table(confuse_matrix,margin = 1) #unsupervised labels关于supervised labels的组成
temp2 <- prop.table(confuse_matrix,margin = 2) #supervised labels关于unsupervised labels的组成

temp[is.na(temp)] <- 0
temp2[is.na(temp2)] <- 0

tempm <- reshape2::melt(temp)

td <- c()
for(i in which(temp>0.7)){
  if(temp2[i] < 0.7){
    td <- append(td,i)
  }
}
tempm <- tempm[td,] #保存点对(unsupervised clusters, supervised clusters)
tempm$value <- NULL

##修改用来构造初始树模型的数据集(ds0)分群
ref_idents <- ds0$seurat_clusters #最开始用来构造树的分类

for(celltype in tempm$true){
  n <- names(ds0$projected_idents[ds0$projected_idents == celltype]) ##需要改变为embedding的细胞
  ref_idents <- factor(ref_idents, levels = c(levels(ref_idents),10+celltype))
  ref_idents[n] <- 10+celltype
  
}
Idents(ds0) <- ref_idents


##用来修正树的数据集(ds2)分群
mod_idents <- ds2$projected_idents
for(celltype in tempm$true){
  n <- names(ds2$seurat_clusters[ds2$seurat_clusters == celltype]) ##需要改变为embedding的细胞
  mod_idents <- factor(mod_idents, levels = c(levels(mod_idents),10+celltype))
  mod_idents[n] <- 10+celltype
}
### ds2的独特细胞类型，判断embedding模式

df <- table(ds0$projected_idents) %>% prop.table()
unique_celltypes <- as.numeric(names(df[df<0.01])) #投射之后少于1%，使用无监督分群
# table(ds0$projected_idents)
for(celltype in unique_celltypes){
  n <- names(ds2$seurat_clusters[ds2$seurat_clusters == celltype]) ##需要改变为embedding的细胞
  mod_idents <- factor(mod_idents, levels = c(levels(mod_idents),20+celltype))
  mod_idents[n] <- 20+celltype
}


# umapplot(ds2,"projected_idents")
Idents(ds2) <- mod_idents

mergeds <- merge(ds0,subset(ds2,idents = "unassigned",invert = T))
levels(Idents(mergeds)) <- c(0:(length(levels(Idents(mergeds)))-1)) ##重命名因子水平
seuobj_label <- as.numeric(as.character(Idents(mergeds))) #原始训练数据

temp <- as.matrix(GetAssayData(mergeds, slot = "data"))
genelist <- GetAssayData(ds0, slot = "var.features")
temp <- temp[genelist, ] # 过滤高变异基因

seuobj_data <- matrix(data = 0, nrow = bst_model$nfeatures, ncol = length(colnames(temp)), 
                   byrow = FALSE, dimnames = list(bst_model[["feature_names"]],colnames(temp)))
intersect_features <- intersect(bst_model[["feature_names"]], rownames(temp))
seuobj_data[intersect_features,] <- temp[intersect_features,]
rm(temp)

## 额外增加的细胞信息

xgb_param <- list(eta = 0.2, max_depth = 6, 
                subsample = 0.6,  num_class = length(table(Idents(mergeds))),
                objective = "multi:softprob", eval_metric = 'mlogloss')


seuobj_train_data <- list(data = t(as(seuobj_data,"dgCMatrix")), label = seuobj_label) 
# use whole dataset as train data
seuobj_train <- xgb.DMatrix(data = seuobj_train_data$data,label = seuobj_train_data$label)
bst_model <- xgb.train(xgb_param, seuobj_train, nrounds = 50, verbose = 0)


ds0 <- XGBoost_predict_from_seuobj(ds0,bst_model)
ds1 <- XGBoost_predict_from_seuobj(ds1,bst_model)
ds2 <- XGBoost_predict_from_seuobj(ds2,bst_model)
```


```{r fig.width=4, fig.height=8}
umapplot(ds0,"projected_idents") /
umapplot(ds1,"projected_idents") /
umapplot(ds2,"projected_idents")


levels(ds0$projected_idents)
```

```{r}
# mergeds <- mergeds %>% SCTransform(vars.to.regress = "percent.mt", verbose = F) %>% 
#     RunPCA() %>% FindNeighbors(dims = 1:20) %>% 
#     RunUMAP(dims = 1:20) %>% 
#     FindClusters(resolution = 0.1)
# 
# umapplot(mergeds,group.by = "Classification1" ,split.by = "orig.ident")
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
